Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-03-16 ms.qmd
Updates

```{r, fig-Methods}
#| label: fig-Methods
#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."

@@

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Mean learning slope in Control = `r format_dec(mean(c(deli_ControlHot, deli_ControlCold)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.025),3)` , `r format_dec(quantile(c(deli_ControlHot, deli_ControlCold), 0.975),3)`] mean learning slope in CORT = `r format_dec(mean(c(deli_CORTHot, deli_CORTCold)),3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.025), 3)` , `r format_dec(quantile(c(deli_CORTHot, deli_CORTCold), 0.975), 3)`], Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold))),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold))), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot))), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold))),3)`), on learning in _L. guichenoti_ (see @fig-results C, D), but we found a significant interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold))), 3)`). However, when the  (Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot) - mean(guich_CORTHot),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlHot) - mean(guich_CORTHot)),3)`) or (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold) - mean(guich_CORTCold),3)`; p~mcmc~ `r format_p(pmcmc(mean(guich_ControlCold) - mean(guich_CORTCold)),3)`).

@@

Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L. delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L. guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L. delicata_ - _L. guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot))), 3)`).

>>>>

```{r, fig-Methods}
#| label: fig-Methods
#| fig.cap: "Experimental design of early environment manipulation and learning tasks. On top, the early environment manipulation for both species. Center, the habituation phase with the respective three different stages. On the bottom, the associative and reversal tasks; white lids show the ramps where the food reward was not accessible."

@@

Both species learnt across all treatments (@fig-results B, D), but we did not find any difference between treatments or species in the rate of learning. For _L. delicata_, hormone treatment (Control - CORT = `r format_dec(mean(c(deli_ControlCold, deli_ControlHot)) - mean(c(deli_CORTCold, deli_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_ControlCold, deli_ControlHot) - c(deli_CORTCold, deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(deli_CORTHot, deli_ControlHot)) - mean(c(deli_CORTCold, deli_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTHot, deli_ControlHot) - c(deli_CORTCold, deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(deli_ControlHot) - mean(deli_CORTHot)) - (mean(deli_ControlCold) - mean(deli_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((deli_ControlHot - deli_CORTHot) - (deli_ControlCold - deli_CORTCold)), 3)`) did not affect learning (see @fig-results A, B). We similarly found no significant effects of  hormone (Control - CORT = `r format_dec(mean(c(guich_ControlCold, guich_ControlHot)) - mean(c(guich_CORTCold, guich_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(guich_ControlCold, guich_ControlHot) - c(guich_CORTCold, guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean(c(guich_CORTHot, guich_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold)),3)`, p~mcmc~ `r format_p(pmcmc(c(guich_CORTHot, guich_ControlHot) - c(guich_CORTCold, guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec((mean(guich_ControlHot) - mean(guich_CORTHot)) - (mean(guich_ControlCold) - mean(guich_CORTCold)), 3)`, p~mcmc~ `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) on learning in _L. guichenoti_ (see @fig-results C, D).

@@

Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (mean of learning slope in _L. delicata_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot), 0.975), 3)`]; mean learning of slope in _L. guichenoti_ = `r format_dec(mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.025), 3)`, `r format_dec(quantile(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot), 0.975), 3)`]; _L. delicata_ - _L. guichenoti_ = `r format_dec(mean(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot)) - mean(c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(deli_CORTCold, deli_ControlCold, deli_CORTHot, deli_ControlHot) - c(guich_CORTCold, guich_ControlCold, guich_CORTHot, guich_ControlHot)), 3)`).
